A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-30 paper.tex
quad

\begin{definition}
A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e. a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism. A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
\end{definition}

@@

\begin{prop}
Fix a volume form $\dvol_M$ on $M$. Suppose $(E, \omega, S)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand. Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$. Suppose the BV action is
\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
where $S_0$ and $S_1$ are independent of $\phi$. Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
\label{prop:integrateoutfield}
\end{prop}

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  Then we define the required perturbative equivalence as follows.  First $F_1(e) = (e, Q_1(e), 0) \in E$.  Then, for $n > 1$, define
\begin{align*}
F_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(F(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
\end{proof}

\begin{remark}
In terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
\[\xymatrix{
\cdots \ar[r] &\mc E_0^0 \ar[r]^{Q_0} \ar[dr] &\mc E_0^1 \ar[r] &\cdots \\
&\cO_M \ar^{i}[r] \ar[ur] &\dens_M &
}\]
where $i$ is the canonical inclusion, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify the differential $Q_0$ and the Lie structure.
\end{remark}

@@

\begin{prop} 
Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
\[
E = E_0 \oplus \left(F \oplus F^! [-1]\right) \oplus \left(F^! \oplus F[-1] \right)
\]
and $\omega$ given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
Suppose further that the action functional
\[
S = S_0 + \int \phi^* \psi - \int \phi I_\phi - \int \psi^* I_{\psi^*} 
\]
satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}$ are local functionals. 
Then, the classical BV theory $(E, \omega, S)$ is equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}$ and $\psi^* = I_{\phi}$ in the original action functional $S$. 
\end{prop}

\begin{proof}
Again, concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ defining 
\[F_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]

The maps $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  
Also, by construction, the $F_n$ intertwine the action functionals, since
\begin{align*}
S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
&= S'(e).
\end{align*}
The linear term $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
\end{proof}

\begin{remark}
Again, in terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
\[\xymatrix{
\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
&&E_1 \ar^{~}[dr] &E_1^! \ar[ur] && \\
&&E_1^! \ar^{~}[ur] &E_1 \ar[uur] && \\
}\]
with the differentials $E_1 \to E_1$ and $E_1^! \to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure.
\end{remark}

@@

\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
\label{sect:4dqgltwist}

>>>>

\begin{definition}
A \defterm{morphism} $\Phi \colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is
% a nonlinear map of vector bundles $E\rightsquigarrow E'$, 
a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism. 
A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
\end{definition}

@@

\begin{prop}\label{prop:integrateoutfield}
Fix a volume form $\dvol_M$ on $M$. Suppose $(E, \omega, S)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand. Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$. Suppose the BV action is
\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
where $S_0$ is a local functional independent of $\phi,\phi^*$ and $S_1$ is a $\cO_M$-valued polydifferential operator which is independent of $\phi$. 
Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set and $\phi = S_1$ and $\phi^* = 0$.
\end{prop}

\begin{remark}
In terms of the classical BV complex, this proposition tells us that if a classical BV complex is of the form
\[\xymatrix{
\cdots & \ul{0} & \ul{1} & \cdots \\
\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar[dr] & E_0^1 \ar[r] &\cdots \\
&\cO_M \ar^{{\rm dvol}}[r] \ar[ur] &\dens_M &
}\]
where the bottom map multiplies a function by the volume element, then we can replace it with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional. 
\end{remark}

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
First $\Psi_1(e) = (e, Q_1(e), 0) \in E$.
For $n > 1$, define
\begin{align*}
\Psi_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $\Psi_n$ manifestly intertwines the pairings $\omega$ and $\omega'$.  
To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(\Psi(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
\end{proof}

@@

\begin{prop} 
\label{prop:BRSTdoublet}
Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
\[
E = E_0 \oplus \left(F \oplus F^! [-1]\right) \oplus \left(F^! \oplus F[-1] \right)
\]
whose sections we denote by $e_0 + \varphi + \varphi^* + \psi + \psi^*$ according to the above decomposition. 
The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
Suppose further that the local functional
\[
S = S_0 + \int \phi \psi^* - \int \phi I_\phi - \int \psi^* I_{\psi^*} 
\]
satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}$ are polydifferential operators on fields valued in $F^!$, $F$ respectively, and which are independent of $\phi$ and $\psi^*$.
Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the original action functional $S$. 
\end{prop}

\begin{remark}
For the classical BV theory $(E, \omega, S)$ as in the proposition, the linearized BV differential defines the following cochain complex of fields:
\[\xymatrix{
\cdots & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \cdots \\
\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
&&F_\phi \ar^{~}[dr] &F^!_{\phi*} \ar[ur] && \\
&&F^!_{\psi^*} \ar^{~}[ur] &F_\psi \ar[uur] && \\
}\]
where the subscripts match the notation for the fields in the statement above. \footnote{Note that we are writing $F$ as if it is concentrated in a single cohomological degree, but the proposition applies for any graded vector bundle as in the statement of the proposition.}
The differentials $F_\phi \to F_\psi$ and $F^!_{\psi^*} \to F^!_{\phi^*}$ are given by the identity.
The arrows from the top line to the bottom lines represent potential $\phi^*$ and $\psi$ dependent terms in $I_\phi, I_{\psi^*}$. 
The above proposition implies we can replace this cochain complex of fields with a quasi-isomorphic complex consisting of only the first line, provided we make a suitable modification of the classical action functional. 
\end{remark}

\begin{proof}
Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
\[\Psi_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]

The maps $\Psi_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $\Psi_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  
Also, by construction, the $\Psi_n$ intertwine the action functionals, since
\begin{align*}
S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(I_{\psi^*}(e), I_\phi(e) - I_\phi(e)) + \omega(I_\phi (e), I_{\psi^*}(e) - I_{\psi^*}(e)) \\
&= S'(e).
\end{align*}
\end{proof}

There is a corollary of this proposition obtained by iterating the procedure. 
We will only use a single iteration.

\begin{cor} \label{cor: quad}
Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
\[
E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
\]
whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
Suppose further that the local functional
\[
S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
\]
satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}$ are polydifferential operators on fields valued in $F^!$, $F$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
\[
E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
\]
and
\[
S' = S_0 + \int \phi_1 \psi_1^* - S''
\]
is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the original action functional $S$.\brian{finish}
\end{cor}
\begin{proof}
%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
We begin by making the following change of coordinates on the BV fields:
\begin{align*}
\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
\end{align*}
with $\phi_1, \psi_1$ left fixed. 
This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
Further, in the new coordinates, the action takes the form
\[
S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
\]
\end{proof}

@@

\begin{proof}
We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
\begin{align*}
& (t \varphi, \rho, t \phi, A_{1,0}) \\
& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
\end{align*}
This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
\begin{align*}
I^{(1)}(Q_t) &= \int \dvol\left(- \wt \chi\wt a^* - t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - t(\Lambda\psi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
&+t\int\dvol\left(\omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* \right) \\
I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
\end{align*}

\end{proof}
\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
\label{sect:4dqgltwist}
